Racial and Ethnic Differences in ETI

### 2023-10-05 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti.qmd
race and eti (numbers look correct to Scott)

---
title: "Racial and Ethnic Differences in ETI"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Dropbox/Miscellaneous/zotero.bib
csl: /Users/timvigers/Dropbox/Miscellaneous/american-medical-association.csl
editor: source
---

@@

```{r data cleaning}
#| include: false
# source("/Users/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_race_eti_analysis_dataset.R")
load("UCD/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/analysis_dataset.RData")
```

@@

```{r}
t1_vars <- c(
  "Gender", "WasGenotyped", "F508_num", "mean_ppFEV", "Age_YrEnd",
  "mean_ppFEV", "weight_last", "weight_perc_last", "bmi_last",
  "bmi_perc_last", "Vx770", "Vx809comb", "Vx661comb", "Vx445comb"
)
```

@@

```{r}
demo %>%
  select(Gender, WasGenotyped, F508_num, race) %>%
  tbl_summary(by = race, missing_text = "Missing") %>%
  bold_labels()
```

>>>>

---
title: "Racial and Ethnic Differences in ETI"
author: "Tim Vigers"
date: "today"
date-format: long
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    code-fold: true
    self-contained: true
    fig-cap-location: top
    page-layout: full
    theme:
      light: flatly
      dark: darkly
bibliography: /Users/timvigers/Documents/Miscellaneous/zotero.bib
csl: /Users/timvigers/Documents/Miscellaneous/american-medical-association.csl
editor: source
---

@@

```{r data cleaning}
#| include: false
# source("/Users/timvigers/GitHub/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/create_race_eti_analysis_dataset.R")
load("/Users/timvigers/Documents/Work/Vigers/CF/Kamyron Jordan/Racial and Ethnic Differences in ETI/Data_Cleaned/analysis_dataset.RData")
```

@@

```{r}
t1_vars <- c(
  "Gender", "F508_num", "mean_ppFEV", "Age_YrEnd",
  "mean_ppFEV", "weight_last", "weight_perc_last", "bmi_last",
  "bmi_perc_last","Vx445comb"
)
```

@@

```{r}
demo %>%
  select(Gender, F508_num, race) %>%
  tbl_summary(by = race, missing_text = "Missing") %>%
  bold_labels()
```
